---
title: "Laundry"
author: "Jeremy Leipzig"
date: "May 10, 2016"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Laundry



```{r load, message=FALSE, warning=FALSE}
library(mlogit)
library(ggplot2)
library(dplyr)
laundryraw<-read.table("LAUNDRY.txt")
```

The laundry detergent data has alternate-row granularity
```{r, message=FALSE, warning=FALSE}


colnames(laundryraw)<-c("panel_id","week","choice","loyal","price","feature","display","alt1","alt2","alt3","obs")
knitr::kable(head(laundryraw))

#there is probably a reshape/tidyr/dplyr method for binary response to categorical but I can't find it
laundryraw %>% mutate(alt = as.factor(ifelse(alt1==1,"alt1",ifelse(alt2==1,"alt2",ifelse(alt3==1,"alt3","def"))))) %>%
mutate(choice = ifelse(choice==2,0,1)) %>% select(-alt1,-alt2,-alt3) %>%
  mutate(week = as.factor(week)) %>%
  mutate(display = as.factor(display)) %>%
  mutate(feature = as.factor(feature)) %>%
  mutate(choice = as.numeric(choice)) %>%
  mutate(obs = as.factor(obs)) %>%
  mutate(panel_id = as.factor(panel_id)) -> laundry
```

mlogit prefers this format:
```{r, message=FALSE, warning=FALSE}
knitr::kable(head(laundry))
```
At first glance how is price a determiniant of choice?
```{r choice, message=FALSE, warning=FALSE}
ggplot(laundry,aes(price))+geom_histogram((aes(fill=as.factor(choice))))
laundry %>% group_by(obs) %>% mutate(rank=rank(price)) %>% filter(choice == 1) %>% ungroup %>% group_by(rank) %>% summarize(ranks=n()) -> price_hist

laundry %>% group_by(obs) %>% summarize(mean_price=mean(price))
ggplot(price_hist,aes(as.factor(rank),ranks))+geom_bar(stat="identity")+xlab("rank")+ylab("occurences of choice 1")
```

Is product feature a determining factor
```{r feature, message=FALSE, warning=FALSE}
laundry %>% group_by(choice,feature) %>% summarize(actual=n()) -> ct_tab
table(laundry$choice,laundry$feature) -> ch_ct
feat_tab<-table(laundry$feature)
```

```{r do_prop_test, message=FALSE, warning=FALSE}
ct_prob<-feat_tab[[2]]/sum(feat_tab)
ct_not<-feat_tab[[1]]/sum(feat_tab)
choice_prob<-.25
choice_not<-.75
ct_tab$expected<-sum(ct_tab$actual)*c(choice_not*ct_not,choice_not*ct_prob,choice_prob*ct_not,choice_prob*ct_prob)
ct_tab$ratio<-round(ct_tab$actual/ct_tab$expected,2)
knitr::kable(ct_tab)
prop.test(ch_ct)
```

Is product display a determining factor?
```{r display, message=FALSE, warning=FALSE}
laundry %>% group_by(choice,display) %>% summarize(actual=n()) -> ct_tab
table(laundry$choice,laundry$display) -> ch_ct
feat_tab<-table(laundry$display)
```

```{r disppretty,ref.label='do_prop_test', message=FALSE, warning=FALSE}
```

## And loyalty?
```{r loyal, message=FALSE, warning=FALSE}
laundry %>% group_by(choice) %>% summarize(mean_loyalty=mean(loyal),sd_loyalty=sd(loyal)) -> loyal_tab
knitr::kable(loyal_tab)
ggplot(laundry,aes(as.factor(choice),loyal))+geom_boxplot()
t.test(laundry %>% filter(choice==1) %>% select(loyal), laundry %>% filter(choice==0) %>% select(loyal))
```

## By week?
```{r week, message=FALSE, warning=FALSE}
ggplot(laundry,aes(week,price))+geom_point(aes(color=as.factor(choice),shape=as.factor(display)))
```

## Using mlogit
```{r mlogit, message=FALSE, warning=FALSE}
#long if each row is an alternate
laundry.mlogit <- 
  mlogit.data(data=laundry, choice="choice", 
              shape="long", 
              alt.levels=c("def","alt1","alt2","alt3"), 
              id.var="obs")
```

A null model of just the the alternates:
```{r nullmodel, message=FALSE, warning=FALSE}
null_model<-mlogit(choice ~ alt, data = laundry.mlogit, method = "nr", probit = FALSE, print.level = 0)
summary(null_model)
```
AIC: `r AIC(null_model)`

A model with the alternates and all marketing features:
```{r marketing, message=FALSE, warning=FALSE}
market_model<-mlogit(choice ~ price + loyal + feature + display, data = laundry.mlogit, method = "nr", probit = FALSE, print.level = 0)

summary(market_model)
```
AIC (smaller is better): `r AIC(market_model)`

A model with the alternates and all marketing features and week:
```{r week_mod, message=FALSE, warning=FALSE}
week_model<-mlogit(choice ~ price + loyal + feature + display | week , data = laundry.mlogit, method = "nr", probit = FALSE, print.level = 0)

summary(week_model)
```
AIC: `r AIC(week_model)`

## What is the value of displays & features
See [Feit's presentation](http://r-marketing.r-forge.r-project.org/slides/chapter13-phillyR/ConjointR20150418.html#/21)
```{r dispvalue, message=FALSE, warning=FALSE}
coef(market_model)["display1"]/(-coef(market_model)["price"])
coef(market_model)["feature1"]/(-coef(market_model)["price"])
coef(market_model)["loyal"]/(-coef(market_model)["price"])
```

The value of a unit of loyalty is very high. Of those 148 instances of '1' loyalty, the favored detergent was selected 134 times.

```{r loybrk, message=FALSE, warning=FALSE}
laundry %>% filter(loyal==1) %>% group_by(choice) %>% summarize(sel=n())
```
